---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ProteoViewer

<!-- badges: start -->
<!-- badges: end -->

The goal of ProteoViewer is to analyse the peptide intensities in a proteomics 
LC-MS/MS experiment. Besides, it provides visualization for the protein topology,
Post-translational modifications and protein Coverage.

## Installation

``` r
# install.packages("devtools")
devtools::install_github("svalvaro/ProteoViewer")
```
## Use the shiny app.

Launch the app locally.

```{r, eval = F}

library(ProteoViewer)

runProteoViewerApp()

```


Or access to it trough the web application hosted at: 
https://proteomics.fgu.cas.cz/ProteoViewer/

## Data

ProteoViewer accepts the `evidence.txt` from [MaxQuant](https://www.maxquant.org/) or the output from 
[Spectronaut](https://biognosys.com/software/spectronaut/)





